From physical principles to ???

### 2016-02-08 2015CompleteDerivation/completeDerivation.tex
Updating status of different sections

%TODO: it would be nice to have "examples" always refer to the same cases, and that they pertain to different type of physics. E.g. trajectory, gravity, thermodynamics, fluid dynamics, biology, electromagnetism...

@@

@@

\begin{justification}
The collection of all possible states forms a set as we can physically distinguish between them.
\end{justification}

>>>>

% Status: Conceptual work done. Text ready for review.

%TODO: incorporate feedback from Dave. Determinism definition as "relative" to choice of state and external processes may need to be reinforced (the single sentence pointing that out is read, forgotten, and then confusion later follows). May want to completely avoid QM at this point. See if can mention without raising further distracting questions.

@@

% Status: concepts still need to be finished. Started to work on linking topology to physically distinguishable states.

%Open questions: smoothness (obviously required to define densities later, is it required in general? What does it means that physical processes/measurements don't give a smooth topology?)

%Things to add: discrete sets evolved continuous = identity map. Subdivide finite interval, same permutation at each time step, exclude odd perms, third-odd perms, ...

@@

\begin{justification}
TODO: all possible states form a set. All possible set of states associated with the outcome of the process form a topology. Verify requirements on entire set, empty set, intersections and unions. Distinguishability of two elements in terms of process outcome leads to Hausdorff. Processes have countable possible outcome means base for topology must be countable, or we would have elements that are not distinguishable, therefore second countability.
\end{justification}
